## NCAA Football Attendance 

Let's load the tidyverse.

```{r}
library(tidyverse)
```

And read in the attendance data:

```{r}
attendance <- read_csv("https://dwillis.github.io/sports-data-files/attendance.csv")
```

Using the tidyverse's `pivot_longer` function, turn the currently wide data into longer data and save it as a new dataframe called `attendance_longer`:

```{r}
attendance_longer <- attendance |> pivot_longer(cols = starts_with("20"), names_to = "Year", values_to = "Attendance")
```

Let's try to figure out whether football attendance has returned to "normal" by 2022, defining "normal" as 2019 figures. For that we'll need to isolate those two years using `filter()` and get rid of any NAs:

```{r}
attendance_two_years <- attendance_longer |> filter(Year %in% c(2019, 2022)) |> na.omit()
```

Now, in order to calculate a percentage change between those two years, we'll need to go back to wider data and again ditch teams where we don't have both years:

```{r}
attendance_wide <- attendance_two_years |> pivot_wider(names_from = Year, values_from = Attendance) |> na.omit()
```

Finally, we'll add a percentage change column to that dataframe (remember, it's (New-Old)/Old) and arrange it to see the results.

```{r}
attendance_wide <- attendance_wide |> mutate(change = 100*(`2022`-`2019`)/`2019`)
```

Some of these clearly are influenced by performance on the field. Below, describe the most interesting results (positive or negative) and what you think might be going on with them. Feel free to do some googling and describe what other data would be helpful to clarify what the best stories here might be. What surprises you about these results?

**ANSWER** Hawaii is fascinating, as their attendance dropped the most. However, they had to change their stadium. Their previous stadium, Aloha Stadium, had a capacity of 50,000. Their new stadium, Ching Complex, had a capacity of 9,000 (they've upgraded it since). Aloha Stadium was deemed unsafe, and was closed during COVID as they could not fund maintenance during these times. Data like team records and attendance percentage (attendance:capacity ratio) would help look at who is filling up seats, but looking at raw attendance numbers is valuable for finding stories such as the Hawaii one. In terms of surprising results, I'm a little surprised to see Maryland's attendance drop over the past three years, especially considering we're better now than we were then. I would've expected at least a small increase.




