```{r}
library(tidyverse)
```


```{r}
w_volleyball_data <- read_csv("https://raw.githubusercontent.com/dwillis/NCAAWomensVolleyballData/main/data/ncaa_womens_volleyball_matchstats_2023.csv")
```


```{r}
conservative_volleyball <- w_volleyball_data |>
  group_by(team) |>
  summarize(
    attack_errors_rate = sum(errors)/sum(total_attacks),
    return_error_rate = sum(r_err)/sum(ret_att),
    block_error_rate = sum(b_err)/sum((block_solos + 0.5*block_assists + b_err))
  )
```



```{r}
conservascore <- conservative_volleyball |>
  mutate(
    z_attack_errors_rate = as.numeric(scale(attack_errors_rate, center = TRUE, scale = TRUE)) * -1,
    z_return_error_rate = as.numeric(scale(return_error_rate, center = TRUE, scale = TRUE)) * -1,
    z_block_error_rate = as.numeric(scale(block_error_rate, center = TRUE, scale = TRUE)) * -1,
    total_z_score = z_attack_errors_rate + z_return_error_rate + z_block_error_rate
  )
```


```{r}
conservascore |>
  select(team, total_z_score) |>
  arrange(desc(total_z_score))
```


As you can see, the highest performing teams by Conservascore are San Diego (record: 6-6), James Madison (10-4), Stephen F. Austin (14-3), Texas (8-3), and Brown (9-2). None of these teams have lost more games than they have won, and most of them win a large majority of the time.


```{r}
conservascore |>
  select(team, total_z_score) |>
  filter(team == "Maryland Terrapins, Terps")
```


Maryland ranks quite high by Conservascore, suggesting that we are either a risk-averse team or are simply very talented. Knowing how often we attempt high-risk but high-value actions would help discern that.


```{r}
conservascore |>
  select(team, total_z_score) |>
  filter(total_z_score < (total_z_score[team == "Maryland Terrapins, Terps"] + .1), total_z_score > (total_z_score[team == "Maryland Terrapins, Terps"] - .1)) |>
  arrange(desc(total_z_score))
```


I had to search how to used Maryland's z score as a basis for finding similar teams. After doing so, I used +/- 0.1 as the "offset" to find a small list of teams similar to Maryland. Teams like Arizona (5-8), Kansas State (8-4), Pittsburgh (11-2), UCLA (8-4), and Colorado (9-4) are near Maryland. These teams are generally good (or at least better than their opposition). However, Maryland this season is 12-3, noticeably better than the teams in this range. This data can be used to show that Maryland's risk-averse approach to volleyball has benefited them so far but could rear its (relatively) ugly head soon. Maybe they should play more aggressively and look for kills where they usually don't, or maybe they don't attempt enough blocks.




Is Colorado due for a resurgence? Despite starting the conference season 1-3, including a 3 game losing streak, the underlying data suggests their results have undersold their performance.

Teams that are fundamentally sound typically do well. This is typically reflected in teams' error rates on actions such as attacks, blocks, and returns. Teams that minimize attack error rate, return error rate, and block error rate tend to do well. Arizona State, Kansas, and Arkansas are three of the best teams in the nation in this regard, and none of these teams have lost more than three games this season. Among Power 5 schools, Colorado is the next best team, yet they've lost more matches than these three teams combined. How come?

Firstly, we can look at some of the teams they lost to. They've lost to UNLV, Kansas, Colorado State, Stanford, UCLA, and USC. We've already noted how good Kansas is, but it should also go without saying that Stanford is quite good as well. Those are two games most would expect Colorado to lose. Thankfully, neither team is still on their schedule. However, they do have to face UCLA and USC again. These are two games, though, that I think they can win next time around. I believe they are as good as these teams if not better. In the loss to UCLA, they suffered from a terrible day hitting-wise, with a hit percentage below 8%. Against USC they were unusually reckless in their returns, committing 11 return errors. These are numbers that are attributable to off days and I don't see them repeating themselves. The games against UNLV and Colorado State were a similar story, and though they already won their reverse matchup against Colorado State they will not have the same opportunity against UNLV.

With 16 games left in the season, the question remains: how will Colorado end the season? With Arizona State, Oregon, and Washington State still on the schedule twice each, I could see them finishing the game 10-6. These are the only teams remaining clearly better than them. The next best teams are UCLA and USC; the rest should be wins for Colorado. They are simply more fundamentally sound than these teams and those teams don't do enough elsewhere to make up for it. Is it a resurgence? A slight one, but given their record against the easier part of their schedule, getting the same results against the tougher half, especially comparing it to their current conference record of 1-3, should be seen as an improvement.