---
title: "Women's Soccer Data"
output: html_notebook
---

We'll use this notebook to explore some NCAA women's soccer data and [our questions](https://docs.google.com/spreadsheets/d/1kTSrnl1URmcexIWLDMWqDnp3q-c2OS45uifnhjp10n4/edit#gid=0). First, let's load the tidyverse library:

```{r}
library(tidyverse)
```

We'll want to start with 2023 match data, which is located in [this GitHub repository](https://github.com/dwillis/NCAAWomensSoccerData). We can load the match data directly from GitHub using `read_csv`:


```{r}
matches_2023 <- read_csv("https://raw.githubusercontent.com/dwillis/NCAAWomensSoccerData/main/data/ncaa_womens_soccer_matchstats_2023.csv")
```

Let's take a look at this data to see what it contains, using `head` and `glimpse`:

```{r}
head(matches_2023)
glimpse(matches_2023)
```

Now, onto the questions using aggregates, which means `group_by` and `summarize`:

1. How many shots in total has Maryland attempted and how many have been on goal? Calculate a percentage of shots on goal.

```{r}
matches_2023 %>%
  filter(team=="Maryland Terrapins, Terps") %>%
  group_by(team) %>%
  summarize(
    total_shots = sum(sh_att),
    shots_on_goal = sum(so_g),
    shot_acc = 100 * shots_on_goal / total_shots
    )
```

2. What about the same shot stats from last season's first four games? You'll need to load the matches from 2022 - just change the season in the URL - and filter by date to find the first four games.

```{r}
matches_2022 <- read_csv("https://raw.githubusercontent.com/dwillis/NCAAWomensSoccerData/main/data/ncaa_womens_soccer_matchstats_2022.csv")
matches_2022 %>%
  filter(team=="Maryland Terrapins, Terps", date < "2022-09-03") %>%
  group_by(team) %>%
  summarize(
      total_shots = sum(sh_att),
      shots_on_goal = sum(so_g),
      shot_acc = shots_on_goal / total_shots
      )
```


3. What about draws - Maryland started 2022 with 4 ties. Have any other teams had as many this season?

```{r}
matches_2023 %>%
  filter(outcome=="Draw") %>%
  group_by(team) %>%
  summarize(
    draws = n()
  ) %>%
  arrange(desc(draws))
```
Plenty of teams had at least 4 ties this season

4. How many total corner kicks has Maryland had so far and how many have its opponents have? Calculate the difference between the two totals for every team.

```{r}
matches_2023 %>%
  group_by(team) %>%
  summarize(
    corners = sum(corners),
    opp_corners = sum(defensive_corners),
    corner_advantage = corners - opp_corners
  ) %>%
  arrange(desc(corner_advantage))
```
I wasn't sure what you exactly meant by "every" team, so I showed the difference for every team. The difference for Maryland specifically, though, is -2 (23 for Maryland, 23 for Maryland's opponents).

## Significance Tests

Hypothesis: There is more scoring in women's soccer this season compared to last season.

Add a column to both dataframes that contains the total_goals for each match. To do this, we'll use mutate and we will save the results back to the same dataframe.

```{r}
matches_2022 <- matches_2022 |> mutate(total_goals = goals + defensive_goals)
matches_2023 <- matches_2023 |> mutate(total_goals = goals + defensive_goals)
```

```{r}
t.test(matches_2022$total_goals, matches_2023$total_goals)
```

The results of this test are strong and usable. However, the difference in goals between the two seasons are small. In 2022, there were 2.7 goals per game. This season, there have been 3 goals per game. Although I do not know the typical variation from year-to-year for goals per game, 0.3 does not seem like a large difference. Also, 2023 is almost exclusively filled with out-of-conference games. These games tend to be more lopsided, and therefore higher scoring. 2022 has more competitive games since it has the full conference season.

```{r}
matches_2022_early <- matches_2022 |> filter(date < "2022-09-14")
t.test(matches_2022_early$total_goals, matches_2023$total_goals)
```

The p-value is still low enough to use the results of the t-test. The results show that there is even less of a difference in scoring between the two seasons, with 2022's early season scoring per game output at 2.9 goals. This is a small, negligible difference.
