I have chosen to attack the first question I posed: "Would ball progression stats like progressive passes and progressive carries be good indicators of how well a team does at creating chances?". Some notes on the data backgrounding:

- the data already exist and can be scraped from fbref.com, though only certain leagues have all the data required
- I can figure out how to scrape the data
- Hopefully, one full season of data would provide a low enough p-value, meaning I would use the 2022-23 season. If it doesn't, however, I will continue adding seasons until I have a strong p-value.
- I will not have to improve/augment the data
- Infogol (https://www.infogol.net/en/blog/analysis/shot-based-expected-goals-models-vs-ball-progression-models) has an expected goals model based on ball progression but it is based on "the historical likelihood that every possession that reached any specific point on the field eventually ended in a goal being scored". What I am attempting to do is to see how progressive actions correlate to chance creation.





```{r}
library(tidyverse)
install.packages("worldfootballR")
library(worldfootballR)
```

```{r}
epl <- fb_match_urls(country = "ENG", gender = "M", season_end_year = c(2018:2024), tier = "1st")
```



```{r}
big5_shooting <- fb_big5_advanced_season_stats(season_end_year = c(2018:2024), stat_type = "shooting", team_or_player = "team") |>
  filter(Team_or_Opponent == "team") |>
  subset(select = -Team_or_Opponent)
big5_passing <- fb_big5_advanced_season_stats(season_end_year = c(2018:2024), stat_type = "passing", team_or_player = "team") |>
  filter(Team_or_Opponent == "team") |>
  subset(select = -Team_or_Opponent)
big5_possession <- fb_big5_advanced_season_stats(season_end_year = c(2018:2024), stat_type = "possession", team_or_player = "team") |>
  filter(Team_or_Opponent == "team") |>
  subset(select = -Team_or_Opponent)
```

```{r}
filtered_big5_shooting <- big5_shooting |>
  group_by(Season_End_Year, Squad) |>
  summarize(non_PK_Gls = Gls_Standard - PK_Standard, Games = Mins_Per_90)

big5_passing |>
  select(Season_End_Year, Squad, PrgP)

big5_possession |>
  select(Season_End_Year, Squad, PrgC_Carries)
```



```{r}
average_big5_shooting <- filtered_big5_shooting |>
  group_by(Season_End_Year) |>
  summarize(mean_non_PK_Gls = sum(non_PK_Gls) / sum(Games))

ggplot() + geom_line(data = filtered_big5_shooting, aes(x = Season_End_Year, y = non_PK_Gls / Games, group = Squad), color = "grey") +
  geom_line(data = average_big5_shooting, aes(x = Season_End_Year, y = mean_non_PK_Gls), color = "red")
```



```{r}
big5 <- data.frame(Season = big5_shooting$Season_End_Year, Club = big5_shooting$Squad, NonPenaltyGoals = filtered_big5_shooting$non_PK_Gls, ProgressivePasses = big5_passing$PrgP, ProgressiveCarries = big5_possession$PrgC_Carries) |>
  mutate(Progressions = ProgressivePasses + ProgressiveCarries) |>
  unite("Squad", Season, Club, remove = TRUE) |>
  mutate(Squad = gsub("_", " ", Squad))
```

I cleaned this up after finding out I could name my columns! I also united the season and club columns. I also fixed a problem I thought I had already fixed before regarding both team and opponent stats showing up.

```{r}
big5_wide <- big5 |>
  pivot_longer(
  cols = starts_with("big5_p"),
  names_to = "Type",
  values_to = "Total_Progressions"
)

ggplot() + geom_bar(
  data = big5_wide,
  aes(x = big5_shooting.Squad, weight = Total_Progressions, fill = Type)
) + coord_flip()
```


The stacked bar chart as of right now is ugly. I am still unsure as to how I want to present this mass of data. I can't decide whether it is continuous (there are years, but they aren't that important because I am not interested in trends over time but rather just need a larger sample size) or categorical (I am finding the relationship between two columns of data). I think it's categorical, but even in that case I am not too sure what I would want to present in a graph. In regards to displaying how much impact progressions have on goal-scoring, I can't think of a way that a bar chart would be helpful.

Another issue is simply the volume of teams. There are 5 leagues. Up until this season, 4 of the 5 leagues had 20 teams, with the Bundesliga being the only one with 18. This year, Ligue 1 went down to 18 teams as well. Across 7 different seasons, this adds up to 684 teams to display data for. I don't think showing an average would suffice, as I want to show a relationship between progressions and goals. Averages would not show a relationship as both progressions and goals have stayed relatively constant over the past seven years.

Small issue I can solve by myself but haven't attempted it yet is finding out how to combine two columns. I assume there is a function for that and I'll need it to combine the Year and Squad columns.

```{r}
fit <- lm(NonPenaltyGoals ~ Progressions, data = big5)
summary(fit)
```

Super-low p-value suggests this data is usable, high r-squared suggests the impact of progressions on non-penalty goals is high. These are good data.

```{r}
ggplot() + geom_point(data = big5, aes(x = Progressions, y = NonPenaltyGoals)) +
  geom_smooth(data = big5, aes(x = Progressions, y = NonPenaltyGoals), method = "lm")
```

Most teams, if not every team—it would be a shame if it was not every team—in the bottom left corner is from the ongoing season, so the data, which is cumulative, are relatively lower. That does not prevent us from seeing the overall trend of the graph. It is well-illustrated that more progressions leads to more goals.

Now that we know that progressions are strongly correlated to goals, more questions can be asked. For example, which form of progressing the ball is more impactful? Carrying or passing?

```{r}
carryfit <- lm(NonPenaltyGoals ~ ProgressiveCarries, data = big5)
passfit <- lm(NonPenaltyGoals ~ ProgressivePasses, data = big5)
summary(carryfit)
summary(passfit)
```

As we can see, both correlations are significant. However, we can tell that progressive passes have more impact on scoring than progressive carries do.

```{r}
ggplot() + geom_point(data = big5, aes(x = ProgressiveCarries, y = NonPenaltyGoals)) +
  geom_smooth(data = big5, aes(x = ProgressiveCarries, y = NonPenaltyGoals), method = "lm")

ggplot() + geom_point(data = big5, aes(x = ProgressivePasses, y = NonPenaltyGoals)) +
  geom_smooth(data = big5, aes(x = ProgressivePasses, y = NonPenaltyGoals), method = "lm")
```

The scatterplots are quite similar and honestly, unless you knew that progressive carries had a larger margin of error than progressive passes, you would not be able to tell by glancing at the graph. However, the margin is slightly bigger.